






\section*{Problem \#16}

\subsubsection*{16.1.A}

The function $f$ is \textbf{not} continuously differentiable due to the discontinuities in the sign function.
\subsubsection*{16.1.B}

The function $f$ \textbf{is} locally Lipschitz, which can be demonstrated by evaluation.
\subsubsection*{16.1.C}

The function $f$ is \textbf{not} continuous on $\R^n$, due to the discontinuity at $x =0$.
\subsubsection*{16.1.D}

The function $f$ \textbf{is} globally Lipschitz, since the derivative of the function is bounded in $\R^n$.
\subsubsection*{16.1.E}

Since the function is globally Lipschitz, the function must also be Uniformly Continuous.

\subsubsection*{16.2.A}

The function $f$ \textbf{is not} continuously differentiable due to the inclusion of the saturation function.

\subsubsection*{16.2.B}

The function $f$ \textbf{is} locally Lipschitz continuous, for a ball $B_r$.

\subsubsection*{16.2.C}

The function $f$ \textbf{is} continuous on $\R^n$ since there are no discontinuities, for the linear, sine, and saturation functions.

\subsubsection*{16.2.D}

The function $f$ is \textbf{is} globally Lipschitz due to the derivative of the linear, sine, and saturation functions being bounded in $\R^n$.

\subsubsection*{16.2.E}
Since the function is globally Lipschitz, it follows that it \textbf{must} be uniformly continuous over $\R^n$.


\subsubsection*{16.3.A}

The function $f$ \textbf{is not} continuously differentiable, due to the saturation function containing non differentiable sharp points.

\subsubsection*{16.3.B}

The function $f$ \textbf{is} locally Lipschitz, since we can find a ball which is a subset of the $\R^n$ such that the Lipschitz condition holds.
\subsubsection*{16.3.C}

The function $f$ is continuous over $\R^n$.
\subsubsection*{16.3.D}

The function $f$ \textbf{is not} globally Lipschitz since, its derivative is not bounded on $\R^n$
\subsubsection*{16.3.E}

The function $f$ is \textbf{not} uniformly continuous, since for a single $\epsilon$ we cannot find a single $\delta$, which satisfy the continuity condition. Hence the function cannot be uniformly continuous.
